---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# foofactors

<!-- badges: start -->
<!-- badges: end -->

The goal of foofactors is to separate a string, but to prevent R from making it a list.

## Installation

You can install the development version of foofactors from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("LaurineSeelt/foofactors")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
# install.packages("devtools")
devtools::install_github("LaurineSeelt/foofactors")
library(foofactors)
(x <- "alfa,bravo,charlie,delta")
str_split_one(x, pattern = ",")
```
<br>
This works better than the example below.
<br>
```{r}
(x <- "alfa,bravo,charlie,delta")
strsplit(x, split = ",")
stringr::str_split(x, pattern = ",")
```
<br>
This returns a list of 1. Thus output is often inconvenient, so the foofactors function solves this.
